
\documentclass{article}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{pgfgantt}
\geometry{a4paper, margin=1in}
\title{6-Month Work Plan for Comparative Analysis of zk-SNARK
Instantiations for Ensuring Ballot Validity}
\author{}
\date{}

\begin{document}

\maketitle

\section{Introduction}
This document outlines the work plan for the project on \textit{Comparative Analysis of zk-SNARK
Instantiations for Ensuring Ballot Validity}. 
The plan spans 6 months and includes time for both research tasks and writing the thesis. 
Each major set of tasks is divided into Work Packages (WP) with specific subtasks. 
Additionally, 2-3 months are allocated for writing the thesis itself. 
The diagram in section \ref{gantt} provides a visual overview of the plan.

\section{Work Packages and Tasks}

\subsection*{WP1: Research and Familiarization (10 weeks)}
\begin{itemize}
    \item \textbf{Task 1.1}: Review literature on Zero-Knowledge Proofs, (Groth16-)SNARKs and representing statements in arithmetic circuits.
    \item \textbf{Task 1.2}: Review literature on Voting systems, election types and ballot validity (especially in connection with zk-SNARKs).
    \item \textbf{Task 1.3}: Research the BN254 elliptic curve.
    \item \textbf{Task 1.4}: Get used to working with Circom.
    \item \textbf{Task 1.5}: Analyze and understand the existing implementation of ballot validity proofs by Huber et. al. in libsnark.
    \item \textbf{Task 1.6 (optional)}: Get used to working with gnark.
    \item \textbf{Task 1.7 (optional)}: Research the BLS12-381 elliptic curve.
\end{itemize}

\subsection*{WP2: Design and Development (12 weeks)}
\begin{itemize}
    \item \textbf{Task 2.1}: Implement the ballot validity proofs from Huber et. al. in Circom using the BN254 curve.
    \item \textbf{Task 2.2 (optional)}: Adapt the ballot validity proofs from Huber et. al. to the BLS12-381 curve and implement those circuits in Circom.
    \item \textbf{Task 2.3 (optional)}: Implement ballot validity proofs from Huber et. al. in gnark using the BLS12-381 and the BN254 curve.
\end{itemize}

\subsection*{WP3: Evaluation (6 weeks)}
\begin{itemize}
    \item \textbf{Task 3.1}: Compare the performance of computing the ballot validity proofs from Huber et. al. in Circom and in Libsnark.
    \item \textbf{Task 3.2 (optional)}: Compare the performance of computing the ballot validity proofs from Huber et. al. in Circom between the two curves BN254 and BLS12-381.
    \item \textbf{Task 3.3 (optional)}: Compare the performance of computing the ballot validits proofy from Huber et. al. in Gnark to Circom and libsnark.
    \item \textbf{Task 3.4}: Document findings (partial write-up to feed into the thesis).
\end{itemize}

\subsection*{WP4: Writing and Presentation (8 weeks)}
\begin{itemize}
    \item \textbf{Task 4.1}: Begin writing the thesis (start drafting during development).
    \item \textbf{Task 4.2}: Complete the thesis write-up, with findings from evaluation.
    \item \textbf{Task 4.3}: Prepare presentation for the defense.
\end{itemize}

\section{Gantt Chart}\label{gantt}

Below is a Gantt chart that visually represents the work packages and their time allocation over the course of 6 months.\\

\noindent\begin{ganttchart}[
    hgrid, 
    vgrid, 
    title height=1,
    bar height=0.6,
    x unit=0.08cm, % Adjust this value to fit the chart on the page
    time slot format=isodate,
    today=2024-11-13
]{2024-11-08}{2025-05-07}
    \gantttitlecalendar{year, month=shortname} \\
    \ganttgroup{WP1}{2024-11-08}{2025-01-17} \\
    % \ganttbar{Task 1.1}{2024-10-01}{2024-10-05} \\
    % \ganttbar{Task 1.2}{2024-10-06}{2024-10-10} \\
    % \ganttbar{Task 1.3}{2024-10-11}{2024-10-15} \\
    
    \ganttgroup{WP2}{2024-12-06}{2025-02-28} \\
    % \ganttbar{Task 2.1}{2024-10-16}{2024-10-30} \\
    % \ganttbar{Task 2.2}{2024-11-01}{2024-11-15} \\
    % \ganttbar{Task 2.3}{2024-11-16}{2024-11-30} \\
    % \ganttbar{Task 2.4}{2024-12-01}{2024-12-15} \\
    
    \ganttgroup{WP3}{2025-01-31}{2025-03-14} \\
    % \ganttbar{Task 3.1}{2024-12-16}{2024-12-31} \\
    % \ganttbar{Task 3.2}{2025-01-01}{2025-01-15} \\
    % \ganttbar{Task 3.3}{2025-01-16}{2025-01-31} \\
    % \ganttbar{Task 3.4}{2025-02-01}{2025-02-15} \\
    
    \ganttgroup{WP4}{2024-12-20}{2025-04-25} \\
    \ganttbar{drafting}{2024-12-20}{2025-02-28} \\
    \ganttbar{writing}{2025-02-28}{2025-04-25} \\
    % \ganttbar{Task 4.3}{2025-03-16}{2025-03-31} \\
    
\end{ganttchart}

\end{document}
